Formalization of Abstract Rewriting

### 2025-06-01 Relations/Paper/Definitions.tex
Counterexamples badly numbered. Only halfway fixed!

\subsection{Closure operators (\texttt{ClosureOperators.agda})}

@@

We next define rewriting-theoretic concepts like confluence and normalization relative to a fixed element of $A$; global versions of these properties are obtained by universal quantification.
\subsection{Normalization (\texttt{ARS-Properties.agda})}
\begin{definition} The following definitions relate to normalization. 
  \begin{description}
    \item[\ule{$\mathbf{a \in \NF_R}$}] \emph{$a$ is a normal form} if $(a,b) \notin R$ for any $b \in A$.
    \item[\ule{$a \in \WN_R$}] \emph{$a$ is weakly normalizing} if $a \mstep b$ for some $b \in \NF_R$.
    \item[\ule{$a \in \SN_R$}] \emph{$a$ is strongly normalizing} if $a$ is accessible with respect to the converse relation $\bar{R} = \setof{(y,x) | (x,y) \in R}$ 
    (see Section \ref{sec:Well-foundedness} for the notion of accessibility).
  \end{description}
\end{definition}

\subsection{Confluence (\texttt{ARS-Properties.agda})}
\begin{definition} The following definitions relate to confluence.
    \begin{description}
        \item[\ule{$a \in \WCR_R$}] \emph{$a$ is weakly Church-Rosser (or weakly confluent)} if $c \bstep a \rstep b \implies c \mstep d \bmstep b$.
        \item[\ule{$a \in \CR_R$}] \emph{$a$ is Church-Rosser (or confluent)} if $c \bmstep a \mstep b \implies c \mstep d \bmstep b$.
        \item[\ule{$a \in \CRs_R$}] \emph{$a$ is subcommutative} if $c \bmstep a \mstep b \implies c \rrstep d \brstep b$.
        \item[\ule{$a \in \NPe_R$}] \emph{$a$ has the conversion normal form property} if $a \estep b \implies a\mstep b$ for any $b \in \NF$.
        \item[\ule{$a \in \NP_R$}] \emph{$a$ has the normal form property} if $c \bmstep a \mstep b \implies c \mstep b$ for any $b \in \NF$.
        \item[\ule{$a \in \UN_R$}] \emph{$a$ has the unique normal form property} if $a \estep b \implies a \equiv b$  for any $a, b \in \NF$.
        \item[\ule{$a \in \UNto_R$}] \emph{$a$ has the unique normal form property with respect to reduction} if $c \bmstep a \mstep b  \implies b \equiv c$  for any $b, c \in \NF$.
    \end{description}
\end{definition}

@@

In \terese $\NF$ is used to denote $\NPe$, whereas we have chosen to use $\NF$ to denote the set of normal forms.

\begin{proposition}\hfill
    \begin{enumerate}
        \item $\gNP \iff \gNPe$
        \item $\gUN \implies \gUNto$
    \end{enumerate}
\end{proposition}
\begin{proof} \hfill
    \begin{enumerate}
        \item \verb|NP₌↔NP : R isNP₌ ↔ R isNP| in \texttt{ARS-Implications.agda}.
        \item \verb|UN→UN→ : R isUN → R isUN→| in \texttt{ARS-Implications.agda}.
    \end{enumerate}
\end{proof}

@@

\subsection{Sequences and Recurrence (\texttt{ARS-Properties.agda}, \texttt{Seq.agda})}
The following definitions are key to formalizing Theorem 1.2.3 in \terese.

@@

In \terese $\mathrm{Ind}$ is used to denote $\BP$.

@@

We wanted to generalize $\RP$ and thought that with $\RPm$ we had a good candidate.
 We show that this weaker definition is
in fact equivalent in the following proof in \texttt{ARS-Implications.agda}:

>>>>

\subsection{Closure operators (\texttt{Closure.agda})}

@@

We next define rewriting-theoretic concepts like confluence and normalization relative to a fixed element of $A$; global versions of these properties are obtained by universal quantification.
\subsection{Normalization (\texttt{Properties.agda})}
\begin{definition} The following definitions relate to normalization. 
  \begin{description}
    \item[\ule{${a \in \NF_R}$}] \emph{$a$ is a normal form} if $(a,b) \notin R$ for any $b \in A$.
    \item[\ule{$a \in \WN_R$}] \emph{$a$ is weakly normalizing} if $a \mstep b$ for some $b \in \NF_R$.
    \item[\ule{$a \in \SN_R$}] \emph{$a$ is strongly normalizing} if $a$ is accessible with respect to the converse relation $\bar{R} = \setof{(y,x) | (x,y) \in R}$ 
    (see Section \ref{sec:Well-foundedness} for the notion of accessibility).
  \end{description}
\end{definition}

\subsection{Confluence (\texttt{Properties.agda})}
\begin{definition} The following definitions relate to confluence.
    \begin{description}
        \item[\ule{$a \in \WCR_R$}] \emph{$a$ is weakly Church-Rosser (or weakly confluent)} if $c \bstep a \rstep b \implies c \mstep d \bmstep b$.
        \item[\ule{$a \in \CR_R$}] \emph{$a$ is Church-Rosser (or confluent)} if $c \bmstep a \mstep b \implies c \mstep d \bmstep b$.
        \item[\ule{$a \in \CRs_R$}] \emph{$a$ is subcommutative} if $c \bmstep a \mstep b \implies c \rrstep d \brstep b$.
        \item[\ule{$a \in \NPe_R$}] \emph{$a$ has the conversion normal form property} if $a \estep b \implies a\mstep b$ for any $b \in \NF$.
        \item[\ule{$a \in \NP_R$}] \emph{$a$ has the normal form property} if $c \bmstep a \mstep b \implies c \mstep b$ for any $b \in \NF$.
        \item[\ule{$a \in \UN_R$}] \emph{$a$ has the unique normal form property} if $a \estep b \implies a \equiv b$  for any $a, b \in \NF$.
        \item[\ule{$a \in \UNto_R$}] \emph{$a$ has the unique normal form property with respect to reduction} if $c \bmstep a \mstep b  \implies b \equiv c$  for any $b, c \in \NF$.
    \end{description}
\end{definition}

@@

In \terese $\,\NF$ is used to denote $\NPe$, whereas we have chosen to use $\NF$ to denote the set of normal forms.

\begin{proposition}\hfill
    \begin{enumerate}
        \item $\gNP \iff \gNPe$
        \item $\gUN \implies \gUNto$
    \end{enumerate}
\end{proposition}
\begin{proof} \hfill
    \begin{enumerate}
        \item \verb|NP₌↔NP : R isNP₌ ↔ R isNP| in \texttt{Implications.agda}.
        \item \verb|UN→UN→ : R isUN → R isUN→| in \texttt{Implications.agda}.
    \end{enumerate}
\end{proof}

@@

\subsection{Sequences and Recurrence (\texttt{Properties.agda}, \texttt{Seq.agda})}
The following definitions are key to formalizing Theorem 1.2.3 in \terese.

@@

In \terese $\mathrm{\,Ind}$ is used to denote $\BP$.

@@

We wanted to generalize $\RP$ and thought that with $\RPm$ we had a good candidate.
 We show that this weaker definition is
in fact equivalent in the following proof in \texttt{Implications.agda}:
